\textsc{RILS}-\textsc{ROLS} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-16 paper_resources/doc/paper.tex
Finished with section 2.

	\section{Problem definition and search space}
	\label{sec:search-space}
	In this section we formally define the SR problem, followed by defining the search space framework of the problem.

	\begin{definition}
		Given is a dataset $D = \{(x_i, y_i)\}_{i=1}^n$, where $\textbf{x} \in \mathbb{R}^d$ represents input variables (features), and $y$ target variable. Suppose that there exists an analytical model of the form $f(\textbf{x})= g^*(\textbf{x}, \theta^*) + \epsilon $ that is a generator of all observations from $D$.  
		The goal of SR is to learn a mapping $\tilde{f}(\textbf{x})=  \tilde{g}(\textbf{x}, \tilde{\theta})  \colon \mathbb{R}^d \mapsto \mathbb{R}$  estimated by searching through the space of (mathematical) expressions  $\tilde{g}$ and parameters $\tilde{\theta}$ where  $\epsilon$ is the presented  white noise within the given input data.

@@

	Koza~\cite{koza1994genetic} introduced the problem of SR as a specific application of genetic programming. GP deals with the object called programs, which need to be optimized. In particular, the programs are represented by syntax trees consisting of functions/operations over input features and constants; as an example of a function represented by a syntax tree, see Figure~\ref{fig:syntax-tree-example} In essence, syntax trees are elements of the search space of SR. That is, each sample model $\tilde{f}$ may be seen as a point in the search space, represented by respective syntax tree. How accurate is this mapping, we compute on the basis of the historical data $D$ and the chosen error   measure (such as $MSE$, or $R^2$). Interestingly, the search space of SR consists of its discrete and continuous part. More precisely, the model we are seeking for might be obtained as a composition of some functions from a (finite) set of mathematical functions. It is common to use the set of the following elementary mathematical functions in the experiments: $\sqrt{x}, x^2 $, $\sin$, $\cos$, $\log$, $\exp$, $\arcsin$, $\arccos$, and $a^x$. It is allowed to link functions will all four operators: $+$, $-$, $\times$, and $/$. After fixing functions that build models, the set of optimal coefficients that  fits to this model must be provided. For the most physical models, these coefficients may receive any real value, that is they are continuous in its nature.

@@

		\caption{Syntax tree representation for the expression $\sin x \times   ( x \times  x / y  )  = \frac{x^2 \sin x }{y}$}
		\label{fig:syntax-tree-example}
	\end{figure}

>>>>

	\section{Problem definition and search space}
	\label{sec:search-space}
	In this section we formally define the SR problem.

	\begin{definition}
		Given is a dataset $D = \{(\mathbf{x_i}, y_i)\}_{i=1}^n$, where $\mathbf{x_i} \in \mathbb{R}^d$ represents i-th feature (input) vector while $y_i \in \mathbb{R}$ is its corresponding target (output) variable. Suppose that there exists an analytical model of the form $f(\mathbf{x})= g^*(\mathbf{x}, \theta^*) + \epsilon $ that is a generator of all observations from $D$.  
		The goal of SR is to learn a mapping $\tilde{f}(\mathbf{x})=  \tilde{g}(\mathbf{x}, \tilde{\theta})  \colon \mathbb{R}^d \mapsto \mathbb{R}$  estimated by searching through the space of (mathematical) expressions  $\tilde{g}$ and parameters $\tilde{\theta}$ where  $\epsilon$ is observed white noise within the given input data.

@@

	Koza~\cite{koza1994genetic} introduced the problem of SR as a specific application of genetic programming. GP can be used to optimize nonlinear structures such as computer programs. In particular, the programs are represented by syntax trees consisting of functions/operations over input features and constants. As an example of a function represented by a syntax tree, see Figure~\ref{fig:syntax-tree-example}. In essence, all valid syntax trees form the solution search space of SR. That is, each sample model $\tilde{f}$ may be seen as a point in the search space, represented by respective syntax tree. The solution accuracy can be computed on the basis of historical data $D$ and the chosen error measure such as $MSE$, $RMSE$, $R^2$, some combination of them, etc. Interestingly, the SR search space nature is twofold: discrete and continuous. It is primarily modeled as a problem of discrete (combinatorial) optimization, since the number of possible solution functional forms is countable. However, it may also include elements solved by means of continuous (global) optimization, e.g., constants (coefficients) fitting. It is common to use the set of the following elementary mathematical functions: $\sqrt{x}, x^2 $, $\sin$, $\cos$, $\log$, $\exp$, $\arcsin$, $\arccos$, $a^x$, and a set of standard arithmetic operators: $+$, $-$, $\times$, and $/$.

@@

		\caption{Syntax tree representation for the expression $\sin{x} \times   ( x \times  x / y  )  = \frac{x^2 \sin x }{y}$}
		\label{fig:syntax-tree-example}
	\end{figure}
